---
title: "Data Science 2 Midterm"
Name: "Jasmin Martinez (JRM2319), Ixtaccihuatl Obregon, Elliot Kim"
Date: "03/24/2025"
output: pdf_document
---

```{r, echo=FALSE}
### Loading Data
load("dat1.RData")
load("dat2.RData")
```

```{r, echo=FALSE}
suppressWarnings({
  suppressPackageStartupMessages({
library(caret)
library(tidymodels)
library(splines)
library(mgcv)
library(pdp)
library(earth)
library(tidyverse)
library(ggplot2)
library(bayesQR) 
library(patchwork)
library(knitr)
library(gratia)
  })
})
```

# Exploratory Analysis
For datasets **dat1** and **dat2** initial exploration of the data structure, descriptive statistics of continuous variables, correlation analysis, and various visualization techniques were conducted. 

<<<<<<< HEAD
Looking at \textbf{dat1}, the distribution of \textbf{log_antibody} is approximately normal, as seen in Figure \ref(fig:d1-log-antibody-hist) and Figure \ref(fig:d1-log-antibody-qq). High and low outliers can be observed in the Figure \@ref(fig:d1-log-antibody-box). Most covariates have weak or low correlation with each other. There is a high positive correlation between \textbf{bmi} and \textbf{weight} ($\rho = 0.72$) and a moderate negative correlation between \textbf{bmi} and \textbf{height} ($\rho = -0.50$). There is a mild negative correlation between \textbf{log_antibody} and \textbf{bmi} ($\rho = -0.23$), \textbf{weight} ($\rho = -0.17$), and \textbf{age} ($\rho = -0.15$). There is a mild positive correlation between \textbf{log_antibody} and \textbf{height} ($\rho = 0.10$). The correlation between \textbf{log_antibody} and \textbf{SBP} ($\rho = -0.06$), \textbf{LDL} ($\rho = -0.04$), and \textbf{time} ($\rho = -0.01$) are near zero, indicating no linear relationship. Linear relationships can be seen in Figure \@ref(fig:d1-log-antibody-lin).

Exploring \textbf{dat2}, the distribution of \textbf{log_antibody} is also approximately normal, as shown Figure \ref(fig:d2-log-antibody-hist) and Figure \ref(fig:d2-log-antibody-qq). High and low outliers are again visible in the Figure \ref(fig:d2-log-antibody-box). Most covariates exhibit weak or low correlation with each other. There is a high positive correlation between \textbf{bmi} and \textbf{weight} ($\rho = 0.72$) and a moderate negative correlation between \textbf{bmi} and \textbf{height} ($\rho = -0.53$). There is a mild negative correlation between \textbf{log_antibody} and \textbf{bmi} ($\rho = -0.16$), \textbf{weight} ($\rho = -0.11$), and \textbf{age} ($\rho = -0.08$). A mild positive correlation exists between \textbf{log_antibody} and \textbf{height} ($\rho = 0.08$). The correlations between \textbf{log_antibody} and \textbf{SBP} ($\rho = -0.01$), \textbf{LDL} ($\rho = -0.00$), and \textbf{time} ($\rho = -0.25$) are near zero or weak, again suggesting no strong linear relationship. Linear relationships can be seen in Figure \ref(fig:d2-log-antibody-lin).
=======
Looking at **dat1**, the distribution of **log_antibody** is approximately normal, as seen in Figure \@ref(fig:d1-log-antibody-hist) and Figure \@ref(fig:d1-log-antibody-qq). High and low outliers can be observed in the Figure \@ref(fig:d1-log-antibody-box). Most covariates have weak or low correlation with each other. There is a high positive correlation between **bmi** and **weight** ($\rho = 0.72$) and a moderate negative correlation between **bmi** and **height** ($\rho = -0.50$). There is a mild negative correlation between **log_antibody** and **bmi** ($\rho = -0.23$), **weight** ($\rho = -0.17$), and **age** ($\rho = -0.15$). There is a mild positive correlation between **log_antibody** and **height** ($\rho = 0.10$). The correlation between **log_antibody** and **SBP** ($\rho = -0.06$), **LDL** ($\rho = -0.04$), and **time** ($\rho = -0.01$) are near zero, indicating no linear relationship. Linear relationships can be seen in Figure \@ref(fig:d1-log-antibody-lin).

Exploring **dat2**, the distribution of **log_antibody** is also approximately normal, as shown Figure \@ref(fig:d2-log-antibody-hist) and Figure \@ref(fig:d2-log-antibody-qq). High and low outliers are again visible in the Figure \@ref(fig:d2-log-antibody-box). Most covariates exhibit weak or low correlation with each other. There is a high positive correlation between **bmi** and **weight** ($\rho = 0.72$) and a moderate negative correlation between **bmi} and **height} ($\rho = -0.53$). There is a mild negative correlation between **log_antibody** and **bmi** ($\rho = -0.16$), **weight** ($\rho = -0.11$), and **age** ($\rho = -0.08$). A mild positive correlation exists between **log_antibody** and **height** ($\rho = 0.084$). The correlations between **log_antibody** and **SBP** ($\rho = -0.01$), **LDL** ($\rho = -0.00$), and **time** ($\rho = -0.25$) are near zero or weak, again suggesting no strong linear relationship. Linear relationships can be seen in Figure \@ref(fig:d2-log-antibody-lin).
>>>>>>> f5e371ff37c9e841cbcaba1343c15e0de86916ee


```{R, eval= FALSE, echo=FALSE}
### Understanding linearity of variables in dat1:
## Observe first couple rows
head(dat1)
str(dat1)
summary(dat1)
```

```{r, message = FALSE, echo=FALSE}
dat1 |>  
  select(where(is.numeric)) |>
  summarise(across(everything(), list(
    Min = min,
    Q1 = ~ quantile(.x, 0.25),
    Median = median,
    Mean = mean,
    Q3 = ~ quantile(.x, 0.75),
    Max = max
  ),
  .names = "{.fn}_{.col}"
  )) |>
   pivot_longer(everything(), names_to = c("Stat", "Variable"), names_sep = "_") |> 
  pivot_wider(names_from = Stat, values_from = value) |>
  kable(caption = "Clean Summary Statistics for Numeric Variables")
```

```{r, eval=FALSE, echo=FALSE}
## Check for missing values
colSums(is.na(dat1))
```

```{r, eval=FALSE, echo=FALSE}
## Check for duplicates
sum(duplicated(dat1))
```

```{r d1-log-antibody-hist, fig.cap="Histogram of log\\_antibody levels for dat1", fig.width=4, fig.height=3, out.width='33%', fig.align='center', echo=FALSE}
## Histogram for distribution of log-transformed antibody levels 
ggplot(dat1, aes(x = log_antibody)) + 
  geom_histogram(bins = 30, fill = "green", alpha = 0.5) + 
  theme_minimal() + 
  labs(title = "Distribution of Log-Antibody Levels",
       x = "Log-Antibody Level",
       y = "Frequency")
```

```{r d1-log-antibody-qq, fig.cap="Q-Q plot of log\\_antibody levels for dat1", fig.width=4, fig.height=3, out.width='33%', fig.align='center', echo=FALSE}
# Q-Q plot
qqnorm(dat1$log_antibody)
qqline(dat1$log_antibody, col = "blue")
```

```{r d1-log-antibody-box, fig.cap="Boxplot of log\\_antibody levels for dat1", fig.width=4, fig.height=3, out.width='33%', fig.align='center', echo=FALSE}
## Assess outliers
ggplot(dat1, aes(y = log_antibody)) +
  geom_boxplot(fill = "blue", alpha = 0.5) + 
  theme_minimal()
```

```{r, eval=FALSE, echo=FALSE}
## Summarize continuous variables
summary(dat1[, c("age", "height", "weight", "bmi", "SBP", "LDL", "time", "log_antibody")])
```

```{R, eval=FALSE, echo=FALSE}
## Assess correlation among continuous variables
cor(dat1[, c("age", "height", "weight", "bmi", "SBP", "LDL", "time", "log_antibody")])
```

```{R d1-log-antibody-lin, fig.cap="Linearity between log\\_antibody levels and covariates for dat1", message=FALSE, echo=FALSE}
## Assess relationship between log_antibody and continuous variables
p1 = ggplot(dat1, aes(x = age, y = log_antibody)) + 
  geom_point(alpha = 0.2, size = 0.5) + 
  geom_smooth(method = "lm", col = "blue") + 
  theme_minimal()

p2 = ggplot(dat1, aes(x = height, y = log_antibody)) + 
  geom_point(alpha = 0.2, size = 0.5) + 
  geom_smooth(method = "lm", col = "blue") + 
  theme_minimal()

p3 = ggplot(dat1, aes(x = weight, y = log_antibody)) + 
  geom_point(alpha = 0.2, size = 0.5) + 
  geom_smooth(method = "lm", col = "blue") + 
  theme_minimal()

p4 = ggplot(dat1, aes(x = bmi, y = log_antibody)) + 
  geom_point(alpha = 0.2, size = 0.5) + 
  geom_smooth(method = "lm", col = "blue") + 
  theme_minimal()

p5 = ggplot(dat1, aes(x = SBP, y = log_antibody)) + 
  geom_point(alpha = 0.2, size = 0.5) + 
  geom_smooth(method = "lm", col = "blue") + 
  theme_minimal()

p6 = ggplot(dat1, aes(x = LDL, y = log_antibody)) + 
  geom_point(alpha = 0.2, size = 0.5) + 
  geom_smooth(method = "lm", col = "blue") + 
  theme_minimal()

p7 = ggplot(dat1, aes(x = time, y = log_antibody)) + 
  geom_point(alpha = 0.2, size = 0.5) + 
  geom_smooth(method = "lm", col = "blue") + 
  theme_minimal()

(p1 | p2 | p3) / (p4 | p5 | p6) / p7
```

```{R, eval=FALSE, echo=FALSE}
## Repeat for dat2
## Observe first couple rows
head(dat2)
str(dat2)
summary(dat2)
```

```{r, eval=FALSE, echo=FALSE}
## Check for missing values
colSums(is.na(dat2))
```

```{r, eval=FALSE, echo=FALSE}
## Check for duplicates
sum(duplicated(dat2))
```

```{r d2-log-antibody-hist, fig.cap="Histogram of log\\_antibody levels for dat2", fig.width=4, fig.height=3, out.width='33%', fig.align='center', echo=FALSE}
## Histogram for distribution of log-transformed antibody levels 
ggplot(dat2, aes(x = log_antibody)) + 
  geom_histogram(bins = 30, fill = "green", alpha = 0.5) + 
  theme_minimal() + 
  labs(title = "Distribution of Log-Antibody Levels",
       x = "Log-Antibody Level",
       y = "Frequency")
```

```{r d2-log-antibody-qq, fig.cap="Q-Q plot of log\\_antibody levels for dat2", fig.width=4, fig.height=3, out.width='33%', fig.align='center', echo=FALSE}
# Q-Q plot
qqnorm(dat2$log_antibody)
qqline(dat2$log_antibody, col = "blue")
```

```{r d2-log-antibody-box, fig.cap="Boxplot of log\\_antibody levels for dat2", fig.width=4, fig.height=3, out.width='33%', fig.align='center', echo=FALSE}
## Assess outliers
ggplot(dat2, aes(y = log_antibody)) +
  geom_boxplot(fill = "blue", alpha = 0.5) + 
  theme_minimal()
```

```{r, eval=FALSE, echo=FALSE}
## Summarize continuous variables
summary(dat2[, c("age", "height", "weight", "bmi", "SBP", "LDL", "time", "log_antibody")])
```

```{R, message = FALSE, eval=FALSE, echo=FALSE}
## Assess correlation among continuous variables
cor(dat2[, c("age", "height", "weight", "bmi", "SBP", "LDL", "time", "log_antibody")])
```

```{R d2-log-antibody-lin, fig.cap="Linearity between log\\_antibody levels and covariates for dat2", message = FALSE, echo=FALSE}
## Assess relationship between log_antibody and continuous variables
p1.2 = ggplot(dat2, aes(x = age, y = log_antibody)) + 
  geom_point(alpha = 0.2, size = 0.5) + 
  geom_smooth(method = "lm", col = "blue") + 
  theme_minimal()

p2.2 = ggplot(dat2, aes(x = height, y = log_antibody)) + 
  geom_point(alpha = 0.2, size = 0.5) + 
  geom_smooth(method = "lm", col = "blue") + 
  theme_minimal()

p3.2 = ggplot(dat2, aes(x = weight, y = log_antibody)) + 
  geom_point(alpha = 0.2, size = 0.5) + 
  geom_smooth(method = "lm", col = "blue") + 
  theme_minimal()

p4.2 = ggplot(dat2, aes(x = bmi, y = log_antibody)) + 
  geom_point(alpha = 0.2, size = 0.5) + 
  geom_smooth(method = "lm", col = "blue") + 
  theme_minimal()

p5.2 = ggplot(dat2, aes(x = SBP, y = log_antibody)) + 
  geom_point(alpha = 0.2, size = 0.5) + 
  geom_smooth(method = "lm", col = "blue") + 
  theme_minimal()

p6.2 = ggplot(dat2, aes(x = LDL, y = log_antibody)) + 
  geom_point(alpha = 0.2, size = 0.5) + 
  geom_smooth(method = "lm", col = "blue") + 
  theme_minimal()

p7.2 = ggplot(dat2, aes(x = time, y = log_antibody)) + 
  geom_point(alpha = 0.2, size = 0.5) + 
  geom_smooth(method = "lm", col = "blue") + 
  theme_minimal()

(p1.2 | p2.2 | p3.2) / (p4.2 | p5.2 | p6.2) / p7.2
```

```{r, fig.width=4, fig.height=3, out.width='80%', fig.align='center',echo=FALSE}
### Assessing lineraity of Dat1
x = model.matrix(log_antibody ~ ., dat1)
y = dat1$log_antibody

theme1 <- trellis.par.get()
theme1$plot.symbol$col <- rgb(.2, .4, .2, .5)
theme1$plot.symbol$pch <- 16
theme1$plot.line$col <- rgb(.8, .1, .1, 1)
theme1$plot.line$lwd <- 2
theme1$strip.background$col <- rgb(.0, .2, .6, .2)

trellis.par.set(theme1)

featurePlot(x[, -c(5, 7)], y, plot = "scatter", labels = c("", "Y"),
type = c("p"), layout = c(3, 2))
```

The exploration and evaluation of **dat1** is used to help build a prediction model specific ally using GAM to understand how demographic and clinical factors influence antibody responses and how antibody levels change over time following vaccination. Considering the researcher collects a new and independent dataset, **dat2**, we discover the correlation between **time** and **log_antibody** is stronger than in **dat1** and similarly has weak linear relationships with most covariates. **Dat2** allows us to evaluate the robustness and generalizability of our prediction model. 

# Model Trainging 
A Generalized Additive Model (GAM) was created to model log-transformed antibody level. Predictors included age, gender, race, smoking, height, weight, BMI, diabetes, hypertension, SBP, LDL, and time since vaccination. To prepare the data for modeling, the model matrix, x, was created using the outcome and all predictors listed above and extracted the response variable, y. Given that race and smoking were categorical variables with multiple categories, some re-coding was necessary to use these variables in the model building. Therefore, race and smoking were converted into factor variables with “White” being the reference group for race and “Never” being the reference group for smoking. 

The GAM models were then fitted. The first model, gam.m1, is a standard linear model with no smoothing terms. The second model, gam.m2, uses smoothing on age, bmi, SBP, LDL, and time since vaccination. There was reason to believe these variables were non-linear, therefore the smoothing allowed the variables to be used in the model. Finally, model 3, gam.m3, includes a tensor product to model the interaction between height and weight. 

The three GAM models were then compared using an ANOVA test that provides the f-test; this was used to determine which model provides the best fit. Cross-validation for GAM tuning was then conducted using a 10-fold cross-validation to tune to GAM model. The best hyperparameters and the final fitted model were then retrieved. The same model training procedure was used with the new, independent dataset, dat2.
```{r, echo=FALSE}
### Creating factors for the Race and Smoking variables to use in the model--for Dat1
dat1$race = factor(dat1$race, 
                         levels = c(1, 2, 3, 4), 
                         labels = c("White", "Asian", "Black", "Hispanic"))

dat1$smoking = factor(dat1$smoking, 
                            levels = c(0, 1, 2), 
                            labels = c("Never", "Former", "Current"))

dat1$race = relevel(dat1$race, ref = "White")
dat1$smoking = relevel(dat1$smoking, ref = "Never")
```

```{r d1-anova-table, fig.cap="ANOVA Comparison of GAM Models (Dat1)" , echo=FALSE}
### Generalized Additive Model (GAM)--Using Dat1 data
set.seed(2)

gam.m1 = gam(log_antibody ~ age + gender + race + smoking + height + weight + bmi + diabetes + hypertension + SBP + LDL + time,
data = dat1)

gam.m2 = gam(log_antibody ~ s(age) + gender + race + smoking + height + weight + s(bmi) + diabetes + hypertension + s(SBP) + s(LDL) + s(time),
data = dat1)

gam.m3 = gam(log_antibody ~ s(age) + gender + race + smoking + te(height, weight) + s(bmi) + diabetes + hypertension + s(SBP) + s(LDL) + s(time),
data = dat1)

anova_result = anova(gam.m1, gam.m2, gam.m3, test = "F")
anova_table = anova(gam.m1, gam.m2, gam.m3, test = "F") |>
  as.data.frame() |>
  dplyr::mutate(Model = c("gam.m1", "gam.m2", "gam.m3")) |>
  dplyr::relocate(Model, .before = 1)
kable(anova_table, caption = "ANOVA Comparison of GAM Models (Dat1)")
```

```{r gam2-gridplot, fig.cap="Smooth terms for GAM model (gam.m2)", echo=FALSE}
#plot(gam.m2)
draw(gam.m2)
```

```{r vis-gam, fig.width=4, fig.height=3, out.width='90%', fig.align='center', fig.cap="Visualization of Model 3 (dat1)", echo=FALSE}
vis.gam(gam.m3, view = c("height","weight"),
color = "topo")
```

```{r, echo=FALSE}
ctrl1 = trainControl(method = "cv", number = 10)
x = dat1[, c("age", "gender", "race", "smoking", "height", "weight", "bmi", 
              "diabetes", "hypertension", "SBP", "LDL", "time")]
y = dat1$log_antibody

set.seed(2)
gam.fit = train(x, y,
method = "gam",
trControl = ctrl1)
tune = gam.fit$bestTune
mod_score = gam.fit$finalModel
```

```{r, fig.width=4, fig.height=3, out.width='80%', fig.align='center', echo=FALSE}
### Assessing linearity of Dat2
x = model.matrix(log_antibody ~ ., dat2)
y = dat2$log_antibody

theme1 <- trellis.par.get()
theme1$plot.symbol$col <- rgb(.2, .4, .2, .5)
theme1$plot.symbol$pch <- 16
theme1$plot.line$col <- rgb(.8, .1, .1, 1)
theme1$plot.line$lwd <- 2
theme1$strip.background$col <- rgb(.0, .2, .6, .2)

trellis.par.set(theme1)

featurePlot(x[, -c(5, 7)], y, plot = "scatter", labels = c("", "Y"),
type = c("p"), layout = c(3, 2))
```

```{r, echo=FALSE}
### Creating factors for the Race and Smoking variables to use in the model--for Dat2
dat2$race = factor(dat2$race, 
                         levels = c(1, 2, 3, 4), 
                         labels = c("White", "Asian", "Black", "Hispanic"))

dat2$smoking = factor(dat2$smoking, 
                            levels = c(0, 1, 2), 
                            labels = c("Never", "Former", "Current"))

dat2$race = relevel(dat2$race, ref = "White")
dat2$smoking = relevel(dat2$smoking, ref = "Never")
```

```{r d2-anova-table, fig.cap="ANOVA Comparison of GAM Models (Dat2)", echo=FALSE}
### Generalized Additive Model (GAM)--Using Dat2 data
set.seed(2)

gam.m1 = gam(log_antibody ~ age + gender + race + smoking + height + weight + bmi + diabetes + hypertension + SBP + LDL + time,
data = dat2)

gam.m2 = gam(log_antibody ~ s(age) + gender + race + smoking + height + weight + s(bmi) + diabetes + hypertension + s(SBP) + s(LDL) + s(time),
data = dat2)

gam.m3 = gam(log_antibody ~ s(age) + gender + race + smoking + te(height, weight) + s(bmi) + diabetes + hypertension + s(SBP) + s(LDL) + s(time),
data = dat2)

anova_result = anova(gam.m1, gam.m2, gam.m3, test = "F")
anova_table = anova(gam.m1, gam.m2, gam.m3, test = "F") |>
  as.data.frame() |>
  dplyr::mutate(Model = c("gam.m1", "gam.m2", "gam.m3")) |>
  dplyr::relocate(Model, .before = 1)
kable(anova_table, caption = "ANOVA Comparison of GAM Models (Dat2)")
```

Model 2 (gam.m2) was chosen to be the final model based on the improvements it made upon Model 1 (gam.m1), (pval=<0.001). 

```{r, echo=FALSE}
#plot(gam.m2)
draw(gam.m2)
```

```{r, fig.width=4, fig.height=3, out.width='90%', fig.align='center', echo=FALSE}
vis.gam(gam.m3, view = c("height","weight"),
color = "topo")
```

# Final Model Results 
```{r, echo=FALSE}
# Model on Dataset 1
ctrl1 = trainControl(method = "cv", number = 10)
x = dat1[, c("age", "gender", "race", "smoking", "height", "weight", "bmi", 
              "diabetes", "hypertension", "SBP", "LDL", "time")]
y = dat1$log_antibody

set.seed(2)
gam.fit = train(x, y,
method = "gam",
trControl = ctrl1)
tune = gam.fit$bestTune
mod_score = gam.fit$finalModel

# Model on Dataset 2
x_test = dat2[, c("age", "gender", "race", "smoking", "height", "weight", "bmi",
                   "diabetes", "hypertension", "SBP", "LDL", "time")]
y_test = dat2$log_antibody
predictions = predict(gam.fit$finalModel, newdata = dat2)
mse = mean((predictions- dat2$log_antibody)^2)
#cat("MSE:", format(mse, nsmall = 3), "\n")

predict_table_d2 = tibble(
  fitted = predictions,
  actual = y_test,
  residual = y_test - predict(gam.fit$finalModel, dat2)
)
```

```{r dx-plots, fig.cap="Diagnostic Plots for Prediction Model on dat2", echo=FALSE}
p1.dx = ggplot(predict_table_d2, aes(x = predictions, y = actual)) +
  geom_point(alpha = 0.5) +
  geom_abline(slope = 1, intercept = 0, color = "blue", linetype = "dashed") +
  theme_minimal() +
  labs(title = "Predicted vs Actual log_antibody Levels",
       x = "Predicted",
       y = "Actual")

p2.dx = ggplot(predict_table_d2, aes(x = predictions, y = residual)) +
  geom_point(alpha = 0.5) +
  geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
  theme_minimal() +
  labs(title = "Residuals vs Predicted",
       x = "Predicted",
       y = "Residual")

p3.dx = ggplot(predict_table_d2, aes(x = residual)) +
  geom_histogram(bins = 30, fill = "steelblue", alpha = 0.7) +
  theme_minimal() +
  labs(title = "Distribution of Residuals", x = "Residual", y = "Count")

p1.dx + p2.dx / p3.dx
```

<<<<<<< HEAD
The prediction model's robustness and generalizability is mostly acceptable for \textbf{dat2}. Prediction accuracy was determined by the mean squared error (MSE) at 0.325 showing a low average on unseen data. The prediction model shows model stability with generalized cross-validation (GCV) score of 0.279. Looking at \ref(fig:dx-plots) we evaluate Predicted vs Actual log_antibody Levels, Residuals vs Predicted, and the Distribution of Residuals. Predictions are mostly aligned with the observed values especially in the 9.5-10.5 predicted range. There is mild under-prediction below value 9, which indicates that the model may tend to underestimate lower antibody levels but perform well in the 9.5-10.5 predicted range. The predicted vs residual plot shows residuals mostly centered and near 0, suggesting that there is no significant bias in the model's predictions. Right-skewness can be observed in the predicted vs residual plots, which could suggest some non-linearity. The distribution of residuals looks approximately normal and does not have extreme outliers or multi-modality. 
=======
The prediction model's robustness and generalizability is mostly acceptable for **dat2**. Prediction accuracy was determined by the mean squared error (MSE) at 0.325 showing a low average on unseen data. prediction model shows model stability with generalized cross-validation (GCV) score of 0.279. The Looking at \@ref(fig:dx-plots) we evaluate Predicted vs Actual log_antibody Levels, Residuals vs Predicted, and the Distribution of Residuals. Predictions are mostly aligned with the observed values especially in the 9.5-10.5 predicted range. There is mild under-prediction below value 9. The predicted vs residual plot shows residuals mostly centered and near 0. Right-skewness can be observed in the predicted vs residual plots, which could suggest some non-linearity. The distribution of residuals looks approximately normal and does not have extreme outliers or multi-modality. 
>>>>>>> f5e371ff37c9e841cbcaba1343c15e0de86916ee



