---
title: "Data Science 2 Midterm"
output: github_document
Name: Jasmin Martinez (JRM2319), Ixtaccihuatl Obregon, Elliot Kim
Date: 03/24/2025
---
### Loading Data
```{r}
load("dat1.RData")
load("dat2.RData")
```

### Understanding linearity of variables in dat1:
```{r}
library(caret)
library(tidymodels)
library(splines)
library(mgcv)
library(pdp)
library(earth)
library(tidyverse)
library(ggplot2)
library(bayesQR) 
```

## Observe first couple rows
```{R}
head(dat1)
str(dat1)
summary(dat1)
```

## Check for missing values
```{r}
colSums(is.na(dat1))
```

## Check for duplicates
```{r}
sum(duplicated(dat1))
```

## Histogram for distribution of log-transformed antibody levels 
```{r}
ggplot(dat1, aes(x = log_antibody)) + 
  geom_histogram(bins = 30, fill = "green", alpha = 0.5) + 
  theme_minimal() + 
  labs(title = "Distribution of Log-Antibody Levels",
       x = "Log-Antibody Level",
       y = "Frequency")
```
## Assess outliers
```{r}
ggplot(dat1, aes(y = log_antibody)) +
  geom_boxplot(fill = "blue", alpha = 0.5) + 
  theme_minimal()
```

## Summarize continuous variables
```{r}
summary(dat1[, c("age", "height", "weight", "bmi", "SBP", "LDL", "time", "log_antibody")])
```

## Assess correlation among continuous variables
```{R}
cor(dat1[, c("age", "height", "weight", "bmi", "SBP", "LDL", "time", "log_antibody")])
```

## Assess relationship between log_antibody and continuous variables
```{R}
ggplot(dat1, aes(x = age, y = log_antibody)) + 
  geom_point(alpha = 0.5) + 
  geom_smooth(method = "lm", col = "blue") + 
  theme_minimal()

ggplot(dat1, aes(x = height, y = log_antibody)) + 
  geom_point(alpha = 0.5) + 
  geom_smooth(method = "lm", col = "blue") + 
  theme_minimal()

ggplot(dat1, aes(x = weight, y = log_antibody)) + 
  geom_point(alpha = 0.5) + 
  geom_smooth(method = "lm", col = "blue") + 
  theme_minimal()

ggplot(dat1, aes(x = bmi, y = log_antibody)) + 
  geom_point(alpha = 0.5) + 
  geom_smooth(method = "lm", col = "blue") + 
  theme_minimal()

ggplot(dat1, aes(x = SBP, y = log_antibody)) + 
  geom_point(alpha = 0.5) + 
  geom_smooth(method = "lm", col = "blue") + 
  theme_minimal()

ggplot(dat1, aes(x = LDL, y = log_antibody)) + 
  geom_point(alpha = 0.5) + 
  geom_smooth(method = "lm", col = "blue") + 
  theme_minimal()

ggplot(dat1, aes(x = time, y = log_antibody)) + 
  geom_point(alpha = 0.5) + 
  geom_smooth(method = "lm", col = "blue") + 
  theme_minimal()
```

## Repeat for dat2

## Observe first couple rows
```{R}
head(dat2)
str(dat2)
summary(dat2)
```

## Check for missing values
```{r}
colSums(is.na(dat2))
```

## Check for duplicates
```{r}
sum(duplicated(dat2))
```

## Histogram for distribution of log-transformed antibody levels 
```{r}
ggplot(dat2, aes(x = log_antibody)) + 
  geom_histogram(bins = 30, fill = "green", alpha = 0.5) + 
  theme_minimal() + 
  labs(title = "Distribution of Log-Antibody Levels",
       x = "Log-Antibody Level",
       y = "Frequency")
```
## Assess outliers
```{r}
ggplot(dat2, aes(y = log_antibody)) +
  geom_boxplot(fill = "blue", alpha = 0.5) + 
  theme_minimal()
```

## Summarize continuous variables
```{r}
summary(dat2[, c("age", "height", "weight", "bmi", "SBP", "LDL", "time", "log_antibody")])
```

## Assess correlation among continuous variables
```{R}
cor(dat2[, c("age", "height", "weight", "bmi", "SBP", "LDL", "time", "log_antibody")])
```

## Assess relationship between log_antibody and continuous variables
```{R}
ggplot(dat2, aes(x = age, y = log_antibody)) + 
  geom_point(alpha = 0.5) + 
  geom_smooth(method = "lm", col = "blue") + 
  theme_minimal()

ggplot(dat2, aes(x = height, y = log_antibody)) + 
  geom_point(alpha = 0.5) + 
  geom_smooth(method = "lm", col = "blue") + 
  theme_minimal()

ggplot(dat2, aes(x = weight, y = log_antibody)) + 
  geom_point(alpha = 0.5) + 
  geom_smooth(method = "lm", col = "blue") + 
  theme_minimal()

ggplot(dat2, aes(x = bmi, y = log_antibody)) + 
  geom_point(alpha = 0.5) + 
  geom_smooth(method = "lm", col = "blue") + 
  theme_minimal()

ggplot(dat2, aes(x = SBP, y = log_antibody)) + 
  geom_point(alpha = 0.5) + 
  geom_smooth(method = "lm", col = "blue") + 
  theme_minimal()

ggplot(dat2, aes(x = LDL, y = log_antibody)) + 
  geom_point(alpha = 0.5) + 
  geom_smooth(method = "lm", col = "blue") + 
  theme_minimal()

ggplot(dat2, aes(x = time, y = log_antibody)) + 
  geom_point(alpha = 0.5) + 
  geom_smooth(method = "lm", col = "blue") + 
  theme_minimal()
```

### Assessing lineraity of Dat1
```{r}
data(dat1)
x = model.matrix(log_antibody ~ ., dat1)
y = dat1$log_antibody

theme1 <- trellis.par.get()
theme1$plot.symbol$col <- rgb(.2, .4, .2, .5)
theme1$plot.symbol$pch <- 16
theme1$plot.line$col <- rgb(.8, .1, .1, 1)
theme1$plot.line$lwd <- 2
theme1$strip.background$col <- rgb(.0, .2, .6, .2)

trellis.par.set(theme1)

featurePlot(x[, -c(5, 7)], y, plot = "scatter", labels = c("", "Y"),
type = c("p"), layout = c(3, 2))
```

### Creating factors for the Race and Smoking variables to use in the model--for Dat1
```{r}
dat1$race = factor(dat1$race, 
                         levels = c(1, 2, 3, 4), 
                         labels = c("White", "Asian", "Black", "Hispanic"))

dat1$smoking = factor(dat1$smoking, 
                            levels = c(0, 1, 2), 
                            labels = c("Never", "Former", "Current"))

dat1$race = relevel(dat1$race, ref = "White")
dat1$smoking = relevel(dat1$smoking, ref = "Never")
```

### Generalized Additive Model (GAM)--Using Dat1 data
```{r}
set.seed(2)

gam.m1 = gam(log_antibody ~ age + gender + race + smoking + height + weight + bmi + diabetes + hypertension + SBP + LDL + time,
data = dat1)

gam.m2 = gam(log_antibody ~ s(age) + gender + race + smoking + height + weight + s(bmi) + diabetes + hypertension + s(SBP) + s(LDL) + s(time),
data = dat1)

gam.m3 = gam(log_antibody ~ s(age) + gender + race + smoking + te(height, weight) + s(bmi) + diabetes + hypertension + s(SBP) + s(LDL) + s(time),
data = dat1)

anova(gam.m1, gam.m2, gam.m3, test = "F")
```

```{r}
plot(gam.m2)
```

```{r}
vis.gam(gam.m3, view = c("height","weight"),
color = "topo")
```

```{r}
ctrl1 = trainControl(method = "cv", number = 10)
x = dat1[, c("age", "gender", "race", "smoking", "height", "weight", "bmi", 
              "diabetes", "hypertension", "SBP", "LDL", "time")]
y = dat1$log_antibody

set.seed(2)
gam.fit = train(x, y,
method = "gam",
trControl = ctrl1)
gam.fit$bestTune
gam.fit$finalModel
```

### Assessing lineraity of Dat2
```{r}
data(dat2)
x = model.matrix(log_antibody ~ ., dat2)
y = dat2$log_antibody

theme1 <- trellis.par.get()
theme1$plot.symbol$col <- rgb(.2, .4, .2, .5)
theme1$plot.symbol$pch <- 16
theme1$plot.line$col <- rgb(.8, .1, .1, 1)
theme1$plot.line$lwd <- 2
theme1$strip.background$col <- rgb(.0, .2, .6, .2)

trellis.par.set(theme1)

featurePlot(x[, -c(5, 7)], y, plot = "scatter", labels = c("", "Y"),
type = c("p"), layout = c(3, 2))
```

### Creating factors for the Race and Smoking variables to use in the model--for Dat2
```{r}
dat2$race = factor(dat2$race, 
                         levels = c(1, 2, 3, 4), 
                         labels = c("White", "Asian", "Black", "Hispanic"))

dat2$smoking = factor(dat2$smoking, 
                            levels = c(0, 1, 2), 
                            labels = c("Never", "Former", "Current"))

dat2$race = relevel(dat2$race, ref = "White")
dat2$smoking = relevel(dat2$smoking, ref = "Never")
```

### Generalized Additive Model (GAM)--Using Dat2 data
```{r}
set.seed(2)

gam.m1 = gam(log_antibody ~ age + gender + race + smoking + height + weight + bmi + diabetes + hypertension + SBP + LDL + time,
data = dat2)

gam.m2 = gam(log_antibody ~ s(age) + gender + race + smoking + height + weight + s(bmi) + diabetes + hypertension + s(SBP) + s(LDL) + s(time),
data = dat2)

gam.m3 = gam(log_antibody ~ s(age) + gender + race + smoking + te(height, weight) + s(bmi) + diabetes + hypertension + s(SBP) + s(LDL) + s(time),
data = dat2)

anova(gam.m1, gam.m2, gam.m3, test = "F")
```

```{r}
plot(gam.m2)
```

```{r}
vis.gam(gam.m3, view = c("height","weight"),
color = "topo")
```

```{r}
ctrl1 = trainControl(method = "cv", number = 10)
x = dat1[, c("age", "gender", "race", "smoking", "height", "weight", "bmi", 
              "diabetes", "hypertension", "SBP", "LDL", "time")]
y = dat1$log_antibody

set.seed(2)
gam.fit = train(x, y,
method = "gam",
trControl = ctrl1)
gam.fit$bestTune
gam.fit$finalModel
```

